Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-29 paper.tex
update

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this serivce queue into a weighted DAG respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.

\subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}. In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of stardard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, all the task-related service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a weighted DAG. In step 7, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Create a weighted DAG from the service queue ( Algorithm\ref{graph_building}) \;
     Calculate the Weighted DAG fitness value\;

@@

Algorithm  \ref{graph_building} is a forward graph buidling algorithm based on \cite{blum1997fast}. This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}. If service queues are sorted resulting in different service order, it is possible to create different corresponding weighted DAGs as composition solutions. In addition. $I_{T}$, $O_{T}$ and $cache$ are also taken as the inputs. Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$.  If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$. This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$. Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking qualities from each satisfied input of $S$. These steps are repeated until all  $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$. Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.

>>>>

Step 3 and Step 4: These two steps follow the standard PSO steps \cite{shi2001particle} except for some differences in particles mapping and decoding processes. In particular, these two differences are related to sorting a created service queue using serivce-to-index mapping for a particle' position vectors and evaluating the fitness of a particle after decoding this service queue into a weighted DAG respectively. Those differences are further addressed in Algorithms \ref{novelSteps} and \ref{graph_building} in \ref{POS-based_algomargin}.

\subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of a PSO-based web service composition algorithm \ref{novelSteps} and a decoding algorithm \ref{graph_building}. In Algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different from those of standard PSO: In step 4, the size of task-related service candidates generated by a greedy search determines the size of each particle's position, and each candidate in a created service candidates queue is mapped to an index of a particle’s position vectors, where each vector has a weight value between 0.0 and 1.0. In step 5, all the task-related service candidates in the queue are sorted according to their corresponding weight values in descending order. In step 6, this sorted queue is used as one of the inputs of the forward decoding algorithm \ref{graph_building} to create a weighted DAG. In step 7, this fitness value of this weighted DAG is the fitness value of the particle calculated by the comprehensive model discussed in \ref{Comprehensive_Quality_Model}.
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Create a service candidates queue and map service candidates to a particle's position vectors\;
     Sort the service queue by position vectors' weights\;
     Create a weighted DAG from the service queue ( Algorithm\ref{graph_building}) \;
     Calculate the Weighted DAG fitness value\;

@@

Algorithm  \ref{graph_building} is a forward graph building algorithm based on \cite{blum1997fast}. This algorithm take one input, a sorted service queue from step 5 of Algorithm \ref{novelSteps}. If service queues are sorted resulting in different service order, it is possible to create different corresponding weighted DAGs as composition solutions. In addition. $I_{T}$, $O_{T}$ and $cache$ are also taken as the inputs. Firstly, $Start$ and $End$ are added to $V$ of $WG$ as an initialisation, and $OutputSet$ is also created with $I_{T}$.  If all the inputs $I_{S}$ of the first popped  $S$ from $queue$ can be satisfied by provided outputs from $OutputSet$. This $S$ is added to $V$ and its outputs are added to $OutputSet$, and $S$ is removed from $queue$. Meanwhile, $e$ is created with its $sm_{e}$ calculated based on the aggregation value of all semantic matchmaking qualities from each satisfied input of $S$. These steps are repeated until all  $O_{T}$ can be satisfied by $Outputset$ or the service queue is $null$. Consequently, this forward graph building technique could lead to more services and edges connected to the $WG$, which should be removed before $WG$ is returned.
